Do We Judge Children's Books by Their Covers? 

### 2024-12-04 paper/paper.qmd
Cleaned formatting error and  typos

```
## Unused Varibles
There are certain variables that could be drawn from the dataset, which may fit the topic of this paper, but will not be used for modeling. In this section we justify why they are not selected. 
### Publication Month
The effect of publication Month have been fully covered by days in a year. While the latter is more accurate.

@@

# Linear Regression Model 
We will first attempt to use linear regression model to predict the average rating of a book.

## Model set-up
For each book, we assumed they are being sampled similarly. \
Let the rating of a book be denoted by $R$. 
Then we will use linear regression model: 
$$
R = \beta_0 + \beta_1P_{day} +  \beta_2P_{day\_in\_year} +\beta_3Pages+\beta_4Reviews+\beta_5Review\_ratio+\beta_6P_{year}+ \epsilon
$$
Where $\epsilon$ is an independent, normally distributed error term.  \
$\beta_0,\beta_1,\beta_2,\beta_3,\beta_4,\beta_5,\beta_6$ are regression coefficients. \
$P_{day}$ is the day in the month. \
$P_{day\_in\_year}$ is the number of day in the year. \
$Pages$ is the number of pages. \
$Reviews$ is the number of text reviews.\
$Review\_ratio$ is the ratio of text reviews.\
$P_{year}$ is the year of publication.\
We will predict the average rating to be: \
$$
\hat{R} = \beta_0 + \beta_1P_{day} +  \beta_2P_{day\_in\_year} +\beta_3Pages+\beta_4Reviews+\beta_5Review\_ratio+\beta_6P_{year}
$$
We fit this model using standard linear regression: finding the set of regression coefficients that minimized mean squared error. 
The model diagnostics are in [Appendix 2](#appendix2)

# Transformer Model
To analysis how title may affect the rating of a book, we use a transformer model to process the title. To implement this model, we used python[@citePython] with supporting packages pytorch[@NEURIPS2019_9015], Scikit-learn[@pedregosa2011scikit], transformers[@wolf-etal-2020-transformers], tqdm[@tqdm], numpy[@harris2020array], and pandas[@mckinney2010data].

@@

### Linear Regression Model

@@

```{r}
#| label: tbl-model
#| tbl-cap: Model summary
#| include: true
#| echo: false
#| warning: false
#| message: false

library(knitr)

model_summary = summary(model)

coef_table <- as.data.frame(model_summary$coefficients)

# Apply formatC to limit to 3 significant figures
coef_table <- as.data.frame(lapply(coef_table, function(x) formatC(x, format = "f", digits = 4)))

colnames(coef_table) <- c("Estimate", "Standard Error", "t value", "p value")

kable(coef_table)
```
#### Note on Publication Year
This variable's effect is not statistically significant, which requires justification for its inclusion in the model. The rationale lies in its role as an underlying factor influencing the Text Reviews Ratio, a key variable associated with higher ratings. There is a clear trend: as the Publication Year approaches the present, the Text Reviews Ratio tends to increase on average, indicating higher levels of reader engagement. This suggests that more recent publications garner greater textual interaction, which, in turn, may positively impact overall ratings.

## BERT regression Model prediction
After some testing, we have decided to train this model on the hyperparameter setting of: MAX_LEN = 30, BATCH_SIZE = 16, EPOCHS = 2, LEARNING_RATE = 0.000013. The model have resulted a mean squared error loss of 0.1271 and R^2 = 0.0794 on test dataset, with mean squared error of 0.1219 on validation dataset. This means that the model explains 7.94% of the variation in average ratings based solely on the book title, suggesting the influence of first impressions on how books are rated.

@@

@@

## Objective
We want to validate and measure the actual effects of three of our main findings:
1. Books expressing themes such as celebration, excitement, gratitude, cheerful, and smile are preferred. While exclamation in the title hints this. 
2. Higher number of pages create positive attitude toward the book.
3. High level of community engagement create positive attitude toward the book.

@@

## Incentives
We will offer the following incentives to complete the survey:
1. A letter explaining the propose, theme and length and possible questions of the survey.

@@

## Survey Structure 
The survey will begin with an introduction explaining its purpose, scope, and confidentiality terms. The participant may continue if they and their guardian fully understands and agrees to the terms and conditions. 
The survey questions will be grouped logically, for children it will covering the topics below:
- Demographics: Collecting background information on participant.
- Reading practices: Amount of reading done by participant lately, which genres and theme is the participant in favor of. Question regarding book length will be in this section. 
- Understanding of Rating: Should book rating reflect experiences apart from reading, such as community engagement?
- Rating of Sample Titles: Several random titles are provided for the participants to rate their first impression. Questions will randomly include real book titles, and book titles with period replace by exclamation marks.
For adults, the "reading practices" section will be replaces by a section collecting the participant's experience with children's book. And the Understanding of Rating will be from a adult perspective, asking questions such as "Will you write reviews based on your chlidren's fondness of the book?"

@@

A sample survey can be found at: https://docs.google.com/forms/d/e/1FAIpQLSeIMsn9aL4JJsZOZtFYFiE_HoZZbaU_g5v84bLXZpoZKjtNpQ/viewform?usp=sf_link.Thank @stantcheva2023surveys and @chen2018methods's paper in providing valuble gudience in creating survey.

>>>>

```
## Unused Varibles
There are certain variables that could be drawn from the dataset, which may fit the topic of this paper, but will not be used for modeling. In this section we justify why they are not selected.

### Publication Month
The effect of publication Month have been fully covered by days in a year. While the latter is more accurate.

@@

## Linear Regression Model 
We will first attempt to use linear regression model to predict the average rating of a book.

### Model set-up
For each book, we assumed they are being sampled similarly. \
Let the rating of a book be denoted by $R$. 
Then we will use linear regression model: 
$$
R = \beta_0 + \beta_1P_{day} +  \beta_2P_{day\_in\_year} +\beta_3Pages+\beta_4Reviews+\beta_5Review\_ratio+\beta_6P_{year}+ \epsilon
$$
Where $\epsilon$ is an independent, normally distributed error term.  \
$\beta_0,\beta_1,\beta_2,\beta_3,\beta_4,\beta_5,\beta_6$ are regression coefficients. \
$P_{day}$ is the day in the month. \
$P_{day\_in\_year}$ is the number of day in the year. \
$Pages$ is the number of pages. \
$Reviews$ is the number of text reviews.\
$Review\_ratio$ is the ratio of text reviews.\
$P_{year}$ is the year of publication.\
We will predict the average rating to be: \
$$
\hat{R} = \beta_0 + \beta_1P_{day} +  \beta_2P_{day\_in\_year} +\beta_3Pages+\beta_4Reviews+\beta_5Review\_ratio+\beta_6P_{year}
$$
We fit this model using standard linear regression: finding the set of regression coefficients that minimized mean squared error. 
The model diagnostics are in [Appendix 2](#appendix2)

## Transformer Model
To analysis how title may affect the rating of a book, we use a transformer model to process the title. To implement this model, we used python[@citePython] with supporting packages pytorch[@NEURIPS2019_9015], Scikit-learn[@pedregosa2011scikit], transformers[@wolf-etal-2020-transformers], tqdm[@tqdm], numpy[@harris2020array], and pandas[@mckinney2010data].

@@

## Linear Regression Model

@@

```{r}
#| label: tbl-model
#| tbl-cap: Linear Regression Model summary
#| include: true
#| echo: false
#| warning: false
#| message: false

model_summary <- summary(model)

coefficients <- as.data.frame(model_summary$coefficients)

coefficients <- coefficients %>%
  mutate_all(~ signif(. , 3))

# Disable scientific notation for 'Estimate' and 'Std. Error' columns
coefficients$Estimate <- format(coefficients$Estimate, scientific = FALSE)
coefficients$`Std. Error` <- format(coefficients$`Std. Error`, scientific = FALSE)

# Rename the predictor variables
rownames(coefficients) <- c("(Intercept)", "Publication Day", "Publication Year", "Number of Pages", "Number of Text Reviews", "Text Review Ratio", "Publication Day in The Year")
colnames(coefficients) = c("	Estimate", "Standard Error", "T value","P value")

kable(coefficients)
```
### Note on Publication Year
This variable's effect is not statistically significant, which requires justification for its inclusion in the model. The rationale lies in its role as an underlying factor influencing the Text Reviews Ratio, a key variable associated with higher ratings. There is a clear trend: as the Publication Year approaches the present, the Text Reviews Ratio tends to increase on average, indicating higher levels of reader engagement. This suggests that more recent publications garner greater textual interaction, which, in turn, may positively impact overall ratings.

## BERT regression Model prediction
After some testing, we have decided on a final model.[@tbl-BERT] shows the final hyperparemeter settings. The model have resulted a mean squared error loss of 0.1271 and R squared of 0.0794 on test dataset, with mean squared error of 0.1219 on validation dataset. This means that the model explains 7.94% of the variation in average ratings based solely on the book title, suggesting the influence of first impressions on how books are rated.

@@

```{r}
#| label: tbl-BERT
#| tbl-cap: hyperparameter setting
#| include: true
#| echo: false
#| warning: false
#| message: false

# Create a data frame with the hyperparameter settings
hyperparameters <- data.frame(
  Hyperparameter = c("MAX_LEN", "BATCH_SIZE", "EPOCHS", "LEARNING_RATE"),
  Value = c(30, 16, 2, 0.000013)
)

hyperparameters$Value[4] <- format(hyperparameters$Value[4], scientific = FALSE)

# Display the table using kable from knitr
kable(hyperparameters)
```

@@

## Objective
We want to validate and measure the actual effects of three of our main findings:

1. Books expressing themes such as celebration, excitement, gratitude, cheerful, and smile are preferred. While exclamation in the title hints this.

2. Higher number of pages create positive attitude toward the book.

3. High level of community engagement create positive attitude toward the book.

@@

## Incentives
We will offer the following incentives to complete the survey:

1. A letter explaining the propose, theme and length and possible questions of the survey.

@@

## Survey Structure 
The survey will begin with an introduction explaining its purpose, scope, and confidentiality terms. The participant may continue if they and their guardian fully understands and agrees to the terms and conditions.

The survey questions will be grouped logically, for children it will covering the topics below:

- Demographics: Collecting background information on participant.

- Reading practices: Amount of reading done by participant lately, which genres and theme is the participant in favor of. Question regarding book length will be in this section.

- Understanding of Rating: Should book rating reflect experiences apart from reading, such as community engagement?

- Rating of Sample Titles: Several random titles are provided for the participants to rate their first impression. Questions will randomly include real book titles, and book titles with period replace by exclamation marks.

For adults, the "reading practices" section will be replaces by a section collecting the participant's experience with children's book. And the Understanding of Rating will be from a adult perspective, asking questions such as "Will you write reviews based on your chlidren's fondness of the book?"

@@

A sample survey can be found at: [Link](https://docs.google.com/forms/d/e/1FAIpQLSeIMsn9aL4JJsZOZtFYFiE_HoZZbaU_g5v84bLXZpoZKjtNpQ/viewform?usp=sf_link).Thank @stantcheva2023surveys and @chen2018methods's paper in providing valuable guidance in creating survey.
